Supplementary Material

### 2025-10-08 manuscript.tex
adjust manuscript

% In this section, we fit the QGP model to quantile forecasts from the 2023-24 CDC flu forecasting competition. 
% Doing this allows for tools to be used to compare forecast performance between models and build ensemble forecasts beyond what is possible using only quantile forecasts \cite[]{mathis2024evaluation,wadsworth2023mixture}.  
In this section, the QGP model is used for QM of quantile forecasts targeting 
US flu hospitalizations. Beginning in 2013, the CDC began hosting a yearly 
forecast competition of the influenza outbreak in the US. This competition is 
known as FluSight. The flu epidemic typically begins in the fall and ends in 
late spring the following year, and the forecast competition lasts around 30 
weeks starting in October and ending in May. FluSight involves several academic 
and industry research teams who each independently develop forecasts  every 
week for predicting certain flu targets for future weeks 
\cite[]{biggerstaff2016results}. During the 2022-23 and 2023-24 seasons, the 
forecast targets were the 1, 2, 3, and 4-week ahead hospitalizations as 
reported by Health and Human Services (HHS) for the 50 US states, Puerto Rico, 
the District of Columbia, and the nation as a whole. The data for weekly 
hospitalizations of flu patients may be found at \cite{healthdata2024covidts}. 
The official guidelines of the most 2023-24 FluSight and all submitted quantile 
forecasts are publicly available at \cite{mathis2023flusight} 
\cite[]{mathis2024evaluation}.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=.5]{Images/flu_horizon_corr.png}
    \caption{Scatterplots of WIS and CRPS values for forecasts from 39 
    different teams for 2023-24 CDC flu forecast competition. The plots are 
    faceted by forecast horizon. Each point represents scores for a flu 
    forecast for one week during the season, one state, and one competing team. 
    Points are transparent to show where more scores tended to be. Overall 
    linear correlation is also given in the corner of each plot.}
    \label{fig:flu_horizon_corr}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=.45]{Images/flu_rank_corr.png}
    \caption{Blocks showing the overall season ranking of 39 competing forecast 
    teams for WIS ($x$-axis) and CRPS ($y$-axis). Blocks on the diagonal line 
    have the same ranking under both scores. Blocks are shaded to show 
    correlation between WIS and CRPS for all forecasts submitted by that team.}
    \label{fig:flu_rank_corr}
\end{figure}

>>>>

% In this section, we fit the QGP model to quantile forecasts from the 2023-24 CDC flu forecasting competition. 
% Doing this allows for tools to be used to compare forecast performance between models and build ensemble forecasts beyond what is possible using only quantile forecasts \cite[]{mathis2024evaluation,wadsworth2023mixture}.  
In this section, the QGP and other models are 
used for QM of quantile forecasts targeting 
US flu hospitalizations. Beginning in 2013, the CDC began hosting a yearly 
forecast competition of the influenza outbreak in the US. This competition is 
known as FluSight. The flu epidemic typically begins in the fall and ends in 
late spring the following year, and the forecast competition lasts around 30 
weeks starting in October and ending in May. FluSight involves several academic 
and industry research teams who each independently develop forecasts  every 
week for predicting certain flu targets for future weeks 
\cite[]{biggerstaff2016results}. During the 2022-23 and 2023-24 seasons, the 
forecast targets were the 1, 2, 3, and 4-week ahead hospitalizations as 
reported by Health and Human Services (HHS) for the 50 US states, Puerto Rico, 
the District of Columbia, and the nation as a whole. The data for weekly 
hospitalizations of flu patients may be found at \cite{healthdata2024covidts}. 
The official guidelines of the most 2023-24 FluSight and all submitted quantile 
forecasts are publicly available at \cite{mathis2023flusight} 
\cite[]{mathis2024evaluation}.

@@

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.5]{Images/all_methods_cwcor.png}}%
    }
    \caption{Scatterplots of WIS and CRPS values for forecasts from 39 
    different teams for 2023-24 CDC flu forecast competition. The plots are 
    faceted by forecast horizon. Each point represents scores for a flu 
    forecast for one week during the season, one state, and one competing team. 
    Points are transparent to show where more scores tended to be. Overall 
    linear correlation is also given in the corner of each plot.}
    \label{fig:flu_horizon_corr}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.45]{Images/all_methods_dists.png}}%
    }
    \caption{Blocks showing the overall season ranking of 39 competing forecast 
    teams for WIS ($x$-axis) and CRPS ($y$-axis). Blocks on the diagonal line 
    have the same ranking under both scores. Blocks are shaded to show 
    correlation between WIS and CRPS for all forecasts submitted by that team.}
    \label{fig:flu_rank_corr}
\end{figure}
